\textbf{Master's Thesis} \\ Correct Projection Mapping on - and Interaction Techniques with - Cloth-based Deformable Surfaces

### 2014-07-22 MSc Report/MScThesis_DanAvram.tex
Completed the section on greedy reconstruction and an introcution that mentions the NURBS-way of tracking a deformable object

There are several techniques for reconstructing a 3D mesh from a point cloud. An important aspect for our deformable display is that we only need a 2.5D correct mesh, similar to a terrain(see figure \ref{fig:PerspectiveTerrain}) or heightmap.

@@

\subsubsection{Greedy Triangulation}
\subsubsection{Kinect Fusion and Kinfu}

>>>>

Before delving into the different methods of object reconstruction, it should be mentioned that there is an alternative to the full reconstruction approach. In \cite{Jordt2011}, a method of tracking deformable objects using depth and color streams is described. The authors of this paper have used a NURBS(Non-uniform rational b-spline - common in computer graphics; can be used to approximate curved surfaces) based deformation function to decouple the geometrical object complexity from the complexity of the deformation. They deform the mesh using a number of control points(low dimensional space when compared to the number of vertices) on the NURBS surface to which the object is mapped. However, it is still needed to have an initial mesh and one way to obtain it is to define a 3D object from the initial frame of the video streams. The desired object can first be segmented out of the frame, and then the 3D vertices can be unprojected to 3D space and connected according to their adjacencies in the depth image(actually, in section \ref{sec:TriangleStripTriangulation} a similar method is used, but it is running on the GPU and updates the mesh every frame). This mesh can be subsequently deformed using the control points, so that it matches the depth and/or color data. The mesh is also mapped to the color image to retrieve the colors of the vertices, but this is not needed for the deformable display, since a texture will be projected onto the mesh, completely replacing any color and lighting information.

Coming back to the general topic of object reconstruction, there are several techniques for reconstructing a 3D mesh from a point cloud. An important aspect for our deformable display is that we only need a 2.5D correct mesh, similar to a terrain(see figure \ref{fig:PerspectiveTerrain}) or heightmap.

@@

\subsubsection{Greedy Triangulation}

Another triangulation method that was briefly considered was the greedy projection algorithm described in \cite{Marton09ICRA}. As described in the previously mentioned source as well as in \cite{navpreet2013}, the algorithm grows the mesh from a list of points, until all points have been considered or there are no more valid triangles to be formed - in case of the latter, the algorithm is restarted somewhere in the unconnected area with vertices from a new \textit{seed} triangle. The triangulation algorithm is of the greedy type(looks for simple solutions to a complex, multi-step problem by deciding which next step will provide the most obvious benefit) and incremental - it considers the neighborhood of the current point and projects it onto the plane that is tangential to the surface formed by the neighborhood. Next, points are pruned(removed if they do not meet certain criteria) by visibility and then, the remaining points are connected to the current point(and consecutive points) by edges, to form triangles. An implementation of the algorithm was readily available, and as such, the algorithm was not studied in detail, although the two previously mentioned sources can be consulted for more information.

An implementation is available in the PCL library, and a description on how to use it can be found in \cite{PCLGreedy}. The algorithm has been tested on the bunny mesh that is mentioned in the PCL tutorial. The result was a triangulated mesh of the provided point cloud. The algorithm also computes the normals and a shaded model of the object is shown in figure \ref{fig:ReconstructedBunny}. However, this was a static object and it was only comprised of about 400 vertices. When the test was run on the point cloud retrieved by the depth camera, the algorithm was running very slow, and it was clear it could not achieve an interactive framerate - it was taking seconds or even minutes per frame, before giving warnings/errors about the dataset; the size of the point cloud was of about 70000 vertices. Indeed, in \cite{Marton09ICRA} it is mentioned that the algorithm is (only) near real-time. Further, a performance analysis is provided, where a point cloud of comparable size was reconstructed in about 9 seconds. Some of the parameters of the algorithm could perhaps be changed in order to improve performance(and remove the warnings), although, it is unlikely that this method will reach an interactive frame rate of about 30 frames per second or more. This is an important aspect to consider, as the distortion of the cloth display needs to update reasonably fast(at interactive speeds) in order for the system to be usable. Due to the previous reason and time constraints, the alternative described in section  \ref{sec:TriangleStripTriangulation} was employed.

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/reconstructedBunny.png}
    \caption{Mesh from point cloud reconstruction of a bunny.}
    \label{fig:ReconstructedBunny}
\end{figure}

\subsubsection{Kinect Fusion and Kinfu}
